Child Poverty Interventions

### 2024-08-02 minos/outcomes/child_poverty_reduction_vis.Rmd
Fixing subdirectory for summaries

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
#out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
# int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReduction',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)

@@

int2.rel_fixed <- int2.rel_fixed #%>%
  #filter(age < 91)

>>>>

```{r, include=FALSE}
#out.path <- here::here('output', 'default_config/')
out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReduction',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
# int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
# int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReduction',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
# int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)

@@

#int2.rel_fixed <- int2.rel_fixed #%>%
  #filter(age < 91)
